---
title: "Coronavirus"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    source_code: embed
    vertical_layout: fill
---

```{r setup, include=FALSE}

rm(list=ls(all.names=TRUE))

#------------------ Packages ------------------
library(flexdashboard)
library(coronavirus)
data(coronavirus)
library(dplyr)
library(tidyr)
library(plotly)
library(DT)


#------------------ Parameters ------------------
# Set colors
# https://www.w3.org/TR/css-color-3/#svg-color
confirmed_color <- "purple"
active_color <- "#1f77b4"
recovered_color <- "forestgreen"
death_color <- "red"

#------------------ Data ------------------


#Since data of coronavirus package is not up to date:
download.file("https://github.com/RamiKrispin/coronavirus/raw/master/data/coronavirus.rda", destfile="cv")
load("cv")

coronavirus <- coronavirus %>% 
  ungroup() %>%
  mutate(country = if_else(Country.Region=="United Arab Emirates","UAE",Country.Region)) %>%
  mutate(country = if_else(country=="Mainland China", "China", country)) %>%
  mutate(country = if_else(country=="North Macedonia", "N.Macedonia", country)) %>%
  mutate(country = if_else(country=="Iran (Islamic Republic of)", "Iran", country)) %>%
  mutate(country = if_else(country=="Republic of Korea", "South Korea", country)) %>%
  mutate(country = if_else(country=="Russian Federation", "Russia", country)) %>%
  mutate(country = if_else(country=="a", "b", country)) %>%
  mutate(country = trimws(country)) %>%
  mutate(country = factor(country))



#Pivot by Country (Rami Krispin)
df <- coronavirus %>% 
  group_by(Country.Region, country, type) %>%
  summarise(total = sum(cases)) %>%
  pivot_wider(names_from =  type, values_from = total, values_fill = list(total=0))  %>%
  mutate(active = confirmed - recovered - death) %>%
  mutate(recover_rate = recovered / confirmed, death_rate = death / confirmed, active_rate = active / confirmed) %>% 
  arrange(-confirmed) %>%
  ungroup()
  
  
  

#Pivot by Country & Date
df1 <- coronavirus %>% 
  group_by(Country.Region, Lat , Long , country, Province.State, date, type) %>%
  summarise(total = sum(cases)) %>%
  pivot_wider(names_from= type, values_from = total, values_fill = list(total=0)) %>%
  mutate(active = confirmed - recovered - death)



df_iran <- df[df$country=='Iran',]



#Trend (Rami Krispin)
df_daily <- coronavirus %>% 
  group_by(date, type) %>%
  summarise(total = sum(cases, na.rm = TRUE)) %>%
  pivot_wider(names_from = type, values_from = total, values_fill = list(total=0)) %>%
  arrange(date) %>%
  ungroup() %>%
  mutate(active =  confirmed - recovered - death) %>%
  mutate(confirmed_cum = cumsum(confirmed),
         death_cum = cumsum(death),
         recovered_cum = cumsum(recovered),
         active_cum = cumsum(active))


  

trend_iran <- coronavirus %>% 
  filter(Country.Region == 'Iran (Islamic Republic of)') %>%
  group_by(date, type) %>%
  summarise(total = sum(cases, na.rm = TRUE)) %>%
  pivot_wider(names_from = type, values_from = total, values_fill = list(total=0)) %>%
  arrange(date) %>%
  ungroup() %>%
  mutate(active =  confirmed - recovered - death) %>%
  mutate(confirmed_cum = cumsum(confirmed),
         death_cum = cumsum(death),
         recovered_cum = cumsum(recovered),
         active_cum = cumsum(active))




max_date <- coronavirus %>% 
  filter(date == max(date)) %>%
  select(Country.Region,country, type, cases) %>%
  group_by(country, type) %>%
  summarise(total = sum(cases)) %>%
  pivot_wider(names_from = type, values_from = total, values_fill = list(total=0)) %>%
  arrange(-confirmed)



min_date <- coronavirus %>%
  group_by(Country.Region) %>%
  summarise(min_date = min(date)) %>%
  arrange(min_date)







```

WORLD {color=red}
=======================================================================

Row
-----------------------------------------------------------------------
  
### confirmed {.value-box}
  
```{r}

valueBox(value = paste(format(sum(df$confirmed), big.mark = ","), "", sep = " "), 
         caption = "Total Confirmed Cases", 
         icon = "fas fa-user-md", 
         color = confirmed_color)
```


### active {.value-box}

```{r}
valueBox(value = paste(format(sum(df$active), big.mark = ",")
                       ," ("
                       ,round(100 * sum(df$active) / sum(df$confirmed), 1)
                       ,"%)"
                       ,sep = ""), 
         caption = "Active Cases", icon = "fas fa-ambulance", 
         color = active_color)
```

### recovered {.value-box}

```{r}
valueBox(value = paste(format(sum(df$recovered), big.mark = ",")
                       ," ("
                       ,round(100 * sum(df$recovered) / sum(df$confirmed), 1) 
                       ,"%)"
                       ,sep = ""), 
         caption = "Recovered Cases", icon = "fas fa-heartbeat", 
         color = recovered_color)
```

### death {.value-box}

```{r}

valueBox(value = paste(format(sum(df$death), big.mark = ",")
                       ," ("
                       ,round(100 * sum(df$death) / sum(df$confirmed), 1)
                       ,"%)"
                       ,sep = ""),
         caption = "Death Cases", 
         icon = "fas fa-heart-broken", 
         color = death_color)
```




Row
-----------------------------------------------------------------------
  
### Cases Distribution by Type (Top 30 Countries)
  
```{r daily_summary}


plot_ly(data = df[1:30,], 
        x = ~ country, 
        y = ~ active, 
        # text =  ~ confirmed, 
        # textposition = 'auto',
        type = "bar", 
        name = "Active",
        marker = list(color = active_color)) %>%
add_trace(y = ~ recovered, 
          # text =  ~ recovered, 
          # textposition = 'auto',
          name = "Recovered",
          marker = list(color = recovered_color)) %>%
add_trace(y = ~ death, 
          # text =  ~ death, 
          # textposition = 'auto',
          name = "Death",
          marker = list(color = death_color)) %>%
layout(barmode = 'stack',
       yaxis = list(title = "", type = "log"),
       xaxis = list(title = "",
                    categoryorder = "array", categoryarray = ~active+recovered+death),
       hovermode = "compare",
       margin =  list(
                   # l = 60,
                   # r = 40,
                   b = 10,
                   t = 10,
                   pad = 2))





```


Row {data-width=350}
-----------------------------------------------------------------------

### Share of Confirmed Cases till `r  max(coronavirus$date)` {data-width=1}

```{r}
df %>%
  select(country, confirmed) %>%
  plot_ly(labels = ~country, 
        values = ~confirmed,
        type = "pie",
        textposition = 'inside',
        textinfo = 'label+percent',
        #hoverinfo = 'text',
        insidetextfont = list(color = '#FFFFFF'),
        showlegend = FALSE)  %>%
  layout(xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
  


```




### Recovery and Death Rates by Country {data-width=3}

```{r}
df_summary <-coronavirus %>% 
  # dplyr::filter(Country.Region != "Others") %>%
  dplyr::group_by(Country.Region, type) %>%
  dplyr::summarise(total_cases = sum(cases)) %>%
  tidyr::pivot_wider(names_from = type, values_from = total_cases) %>%
  dplyr::arrange(- confirmed) %>%
  dplyr::filter(confirmed >= 25) %>%
  dplyr::select(country = Country.Region, confirmed, recovered, death) %>%
  dplyr::mutate(recover_rate = recovered / confirmed,
                death_rate = death / confirmed)  
df_summary %>%
  DT::datatable(rownames = FALSE,
                colnames = c("Country", "Confirmed", "Recovered", "Death", "Recovery Rate", "Death Rate"),
                options = list(pageLength = nrow(df_summary), dom = 'tip')) %>%
  DT::formatPercentage("recover_rate", 2) %>%
  DT::formatPercentage("death_rate", 2) 
```


### Share of Death Cases till `r  max(coronavirus$date)` {data-width=1}

```{r}
df %>%
  select(country, death) %>%
  plot_ly(labels = ~country, 
        values = ~death,
        type = "pie",
        textposition = 'inside',
        textinfo = 'label+percent',
        #hoverinfo = 'text',
        insidetextfont = list(color = '#FFFFFF'),
        showlegend = FALSE)  %>%
  layout(xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
  


```



Trend
=======================================================================

 Row
-----------------------------------------------------------------------


### Daily Cumulative Cases
  
```{r}


plot_ly(data = df_daily) %>%
    add_trace(x = ~ date,
            y = ~ confirmed_cum,
            type = "scatter",
            mode = 'lines+markers',
            name = "Confirmed",
            line = list(color = confirmed_color),
            marker = list(color = confirmed_color)) %>%
  add_trace(x = ~ date,
            y = ~ active_cum,
            type = "scatter",
            mode = "lines+markers",
            name = "Active",
            line = list(color = active_color),
            marker = list(color = active_color)) %>%
  add_trace(x = ~ date,
            y = ~ recovered_cum,
            type = "scatter",
            mode = "lines+markers",
            name = "Recovered",
            line = list(color = recovered_color),
            marker = list(color = recovered_color)) %>%
  add_trace(x = ~ date,
            y = ~ death_cum,
            type = "scatter",
            mode = 'lines+markers',
            name = "Death",
            line = list(color = death_color),
            marker = list(color = death_color)) %>%
  add_annotations(x = as.Date("2020-03-01"),
                  y = 42716,
                  text = paste("# of recovered cases surpass", 
                               "", 
                               "the # of active cases"),
                  xref = "x",
                  yref = "y",
                  arrowhead = 5,
                  arrowhead = 3,
                  arrowsize = 1,
                  showarrow = TRUE,
                  ax = -10,
                  ay = 90) %>%
  layout(title = "",
         yaxis = list(title = "Cumulative No. of Cases"),
         xaxis = list(title = ""),
         legend = list(x = 0.1, y = 0.9),
         hovermode = "compare")

```





### Daily New Confirmed Cases - China vs. Rest of the World

```{r}
daily_confirmed <- coronavirus %>%
  filter(type == "confirmed") %>%
  mutate(country = dplyr::if_else(Country.Region == "Mainland China", 
                                  "China", 
                                  "Rest of the World")) %>%
  group_by(date, country) %>%
  summarise(total = sum(cases)) %>% 
  ungroup() %>%
  pivot_wider(names_from = country, values_from = total) 

#----------------------------------------
# Plotting the data

daily_confirmed %>%
  plot_ly() %>% 
  add_trace(x = ~ date, 
            y = ~ China, 
            type = "scatter", 
            mode = "lines+markers",
            name = "China") %>% 
  add_trace(x = ~ date, 
            y = ~ `Rest of the World`, 
            type = "scatter", 
            mode = "lines+markers",
            name = "Rest of the World") %>% 
  add_annotations(x = as.Date("2020-02-13"),
                  y = 15133,
                  text = paste("China modified the diagnostic criteria"),
                  xref = "x",
                  yref = "y",
                  arrowhead = 5,
                  arrowhead = 3,
                  arrowsize = 1,
                  showarrow = TRUE,
                  ax = 50,
                  ay = -40) %>%
  layout(title = "",
         legend = list(x = 0.1, y = 0.9),
         yaxis = list(title = "Number of New Cases"),
         xaxis = list(title = ""),
         # paper_bgcolor = "black",
         # plot_bgcolor = "black",
         # font = list(color = 'white'),
         hovermode = "compare",
         margin =  list(
                        # l = 60,
                        # r = 40,
                        b = 10,
                        t = 10,
                        pad = 2
                 ))

```





Row
-----------------------------------------------------------------------


### Recovery and Death Rates for Countries with at Least 25 Cases
  
```{r}
  
df %>%
  filter(confirmed >= 25) %>%
  
  plot_ly(y = ~ round(100 * recover_rate, 1),
          x = ~ round(100 * death_rate, 1),
          size = ~ log(confirmed),
          sizes = c(5, 70),
          type = 'scatter', mode = 'markers',
          color = ~ country,
          marker = list(sizemode = 'diameter' , opacity = 0.5),
          hoverinfo = 'text',
          text = ~paste("", country, 
                        " Confirmed Cases: ", confirmed,
                        " Recovery Rate: ", paste(round(100 * recover_rate, 1), "%", sep = ""),
                        " Death Rate: ",  paste(round(100 * death_rate, 1), "%", sep = ""))) %>%
  layout(yaxis = list(title = "Recovery Rate", ticksuffix = "%"),
         xaxis = list(title = "Death Rate", ticksuffix = "%", 
                      dtick = 1, 
                      tick0 = 0),
         hovermode = "compare")

```   


### Number of Countries with at Least 1 Active Case at the Time
  
```{r}

df1 %>%
  ungroup() %>%
  select(date, country, active) %>%
  arrange(country, date) %>%
  mutate(activ_cum=ave(active, country, FUN=cumsum)) %>%
  filter(activ_cum>0) %>%
  select(date, country) %>%
  mutate(duplicate = duplicated(.)) %>%
  filter(duplicate==F) %>%
  group_by(date) %>%
  summarise(No.Countries =  n()) %>%
  arrange(date) %>%
  
  
  plot_ly(x = ~ date, 
          y = ~ No.Countries, 
          type = "scatter", 
          mode = "lines+markers",
          name = "No.Countries") %>% 
  layout(yaxis = list(title = 'Number of Countires'),
         hovermode = "compare")

  

``` 


Today
=======================================================================


Row
-----------------------------------------------------------------------

### New Confirmed Cases on `r  max(coronavirus$date)` - Top 15 Countries
  
```{r}
df1 %>% 
  filter(date==max(coronavirus$date)) %>% 
  ungroup() %>%
  select(country, confirmed) %>% 
  arrange(-confirmed) %>% 
  top_n(n = 15, wt = confirmed) %>%
  
  plot_ly(x = ~ country,
          y = ~ confirmed,
          text = ~ confirmed,
          textposition = 'auto',
          type = "bar") %>%
  layout(yaxis = list(title = ""), #paste("Confirmed Cases on ", max(coronavirus$date))),
         xaxis = list(title = "",
                      categoryorder = "array", categoryarray = ~confirmed),
         margin =  list(
         l = 10,
         r = 10,
         b = 10,
         t = 10,
         pad = 2
         ))


```


### Cases Status Update for `r  max(coronavirus$date)`

```{r}
df1 %>% 
  ungroup() %>%
  filter(date==max(date)) %>%
  select(country, confirmed, recovered, death) %>%
  arrange(-confirmed) %>%
  
  DT::datatable(rownames = FALSE,
                colnames = c("Country", "Confirmed", "Recovered", "Death"),
                options = list(pageLength = 10, dom = 'tip'),
                )

```



Row
-----------------------------------------------------------------------

### 222

```{r}

```


### 333

```{r}

```




Map
=======================================================================

<center>Coronavirus Confirmed Cases Worldwide</center>

```{r}

# light grey boundaries
l <- list(color = toRGB("grey"), width = 0.1)

# specify map projection/options
g <- list(
  showframe = FALSE,
  showcoastlines = FALSE,
  projection = list(type = 'Mercator')
)

df %>%
  plot_geo(z = ~ log(confirmed), 
           color = ~ confirmed, 
           colors = 'Purples',
           text = ~ paste(country, ' >> ', confirmed), 
           hoverinfo = 'text',
           locations = ~ country , 
           locationmode = 'country names',
           marker = list(line = l)) %>%

  #colorbar(title = 'Confirmed Cases', tickprefix = '') %>%
  hide_colorbar() %>% 
  layout(geo = g)
         #title = '2014 Global GDP<br>Source:<a href="https://www.cia.gov/library/publications/the-world-factbook/fields/2195.html">CIA World Factbook</a>'




```


IRAN
=======================================================================



Row
-----------------------------------------------------------------------

### confirmed {.value-box}
  
```{r}

valueBox(value = paste(format(sum(df_iran$confirmed), big.mark = ","), "", sep = " "), 
         caption = "Total Confirmed Cases", 
         icon = "fas fa-user-md", 
         color = confirmed_color)
```


### active {.value-box}

```{r}
valueBox(value = paste(format(sum(df_iran$active), big.mark = ",")
                       ," ("
                       ,round(100 * sum(df_iran$active) / sum(df_iran$confirmed), 1)
                       ,"%)"
                       ,sep = ""), 
         caption = "Active Cases", icon = "fas fa-ambulance", 
         color = active_color)
```

### recovered {.value-box}

```{r}
valueBox(value = paste(format(sum(df_iran$recovered), big.mark = ",")
                       ," ("
                       ,round(100 * sum(df_iran$recovered) / sum(df_iran$confirmed), 1) 
                       ,"%)"
                       ,sep = ""), 
         caption = "Recovered Cases", icon = "fas fa-heartbeat", 
         color = recovered_color)
```

### death {.value-box}

```{r}

valueBox(value = paste(format(sum(df_iran$death), big.mark = ",")
                       ," ("
                       ,round(100 * sum(df_iran$death) / sum(df_iran$confirmed), 1)
                       ,"%)"
                       ,sep = ""),
         caption = "Death Cases", 
         icon = "fas fa-heart-broken", 
         color = death_color)
```



 Row
-----------------------------------------------------------------------


### Daily Cumulative Cases in Iran {data-width=4}
  
```{r}

df1 %>%
  ungroup() %>%
  filter(country=='Iran') %>%
  select(date, recovered, death, active) %>%
  mutate(recovered_cum=cumsum(recovered),
         death_cum=cumsum(death),
         active_cum=cumsum(active)) %>%

  plot_ly(x = ~ date,
          y = ~ active_cum,
          type = "scatter",
          mode = "lines+markers",
          name = "Active",
          line = list(color = active_color),
          marker = list(color = active_color)) %>%
  add_trace(x = ~ date,
            y = ~ recovered_cum,
            type = "scatter",
            mode = "lines+markers",
            name = "Recovered",
            line = list(color = recovered_color),
            marker = list(color = recovered_color)) %>%
  add_trace(x = ~ date,
            y = ~ death_cum,
            type = "scatter",
            mode = 'lines+markers',
            name = "Death",
            line = list(color = death_color),
            marker = list(color = death_color)) %>%
  layout(title = "",
         yaxis = list(title = "Cumulative No. of Cases"),
         xaxis = list(title = ""),
         legend = list(x = 0.1, y = 0.9),
         hovermode = "compare")

```




### Population (www.worldometers.info) {data-width=2}
```{r}

as.data.frame(cbind(c('China','Iran','Italy','South Korea'),
                    c('1439','84','60','51'))) %>%
  DT::datatable(class='compact',
            colnames = c('Country', 'Population in Millions'),
            options = list(sDom = '<"top"><"bottom">'))



```



### Cumulative Confirmed Cases - Top 3 Countries Excluding China {data-width=4}
```{r}

#top <- df %>%
#  filter(country!='China') %>%
#  arrange(-confirmed) %>%
#  top_n(3, wt=confirmed) %>%
#  select(country)

df1 %>%
  ungroup() %>%
  #filter(country %in% unlist(top)) %>%
  filter(country %in% c('Iran', 'Italy', 'South Korea')) %>%
  select(country, date, confirmed) %>%
  arrange(country, date) %>%
  mutate(confirmed_cum = ave(confirmed, country, FUN=cumsum)) %>%
  select(country, date, confirmed_cum) %>%
  pivot_wider(names_from = country,
              values_from = confirmed_cum,
              values_fill=list(confirmed_cum=0)) %>%
  arrange(date) %>%


  plot_ly(x = ~ date,
          y = ~ Iran,
          type = "scatter",
          mode = "lines+markers",
          name = "Iran",
          line = list(color = 'green'),
          marker = list(color = 'green')) %>%
  
  add_trace(x = ~ date, 
            y = ~ Italy, 
            type = "scatter", 
            mode = "lines+markers",
            name = "Italy",
            line = list(color = 'blue'),
            marker = list(color = 'blue')) %>% 
  
  add_trace(x = ~ date, 
            y = ~ `South Korea`, 
            type = "scatter", 
            mode = "lines+markers",
            name = "South Korea",
            line = list(color = 'red'),
            marker = list(color = 'red')) %>% 

  layout(title = "",
         yaxis = list(title = "Cumulative Confirmed Cases"),
         xaxis = list(title = ""),
         legend = list(x = 0.1, y = 0.9),
         hovermode = "compare")




```




 Row
-----------------------------------------------------------------------

### 123

```{r}


```


### 123
```{r}

```


Data
=======================================================================

```{r}
df1 %>% 
  ungroup() %>%
  select(date, country, Province.State, confirmed, recovered, death) %>%
  DT::datatable(rownames = FALSE,
                options = list(searchHighlight = TRUE, pageLength = 20), 
                filter = 'top')
```



About
=======================================================================
  
  **The Coronavirus Dashboard**
  
  This Coronavirus dashboard provides an overview of the 2019 Novel Coronavirus COVID-19 (2019-nCoV) epidemic. This dashboard is built with R using the Rmakrdown framework and can easily reproduce by others. The code behind the dashboard available [here](https://github.com/RamiKrispin/coronavirus_dashboard)

**Data**
  
  The input data for this dashboard is the [coronavirus](https://github.com/RamiKrispin/coronavirus) R package (dev version). The data and dashboard is refreshed on a daily bases. The raw data pulled from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus [repository](https://github.com/RamiKrispin/coronavirus-csv)




**Packages**
  
  * Dashboard interface - the [flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/) package. 
* Visualization - the [plotly](https://plot.ly/r/) package
* Data manipulation - [dplyr](https://dplyr.tidyverse.org/), and [tidyr](https://tidyr.tidyverse.org/)
* Tables - the [DT](https://rstudio.github.io/DT/) package

**Deployment and reproducibly**
  
  The dashboard was deployed to Github docs. If you wish to deploy and/or modify the dashboard on your Github account, you can apply the following steps:
  
  * Fork the dashboard [repository](https://github.com/RamiKrispin/coronavirus_dashboard), or
* Clone it and push it to your Github package
* Here some general guidance about deployment of flexdashboard on Github page - [link](https://github.com/pbatey/flexdashboard-example)

For any question or feedback, you can either open an [issue](https://github.com/RamiKrispin/coronavirus_dashboard/issues) or contact me on [Twitter](https://twitter.com/Rami_Krispin).



