---
title: "Coronavirus"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    source_code: embed
    vertical_layout: fill
---

```{r setup, include=FALSE}

rm(list=ls(all.names=TRUE))

#------------------ Packages ------------------
library(flexdashboard)
library(coronavirus)
data(coronavirus)
library(dplyr)
library(tidyr)
library(plotly)
library(DT)


#------------------ Parameters ------------------
# Set colors
# https://www.w3.org/TR/css-color-3/#svg-color
confirmed_color <- "purple"
active_color <- "#1f77b4"
recovered_color <- "forestgreen"
death_color <- "red"

#------------------ Data ------------------


#Since data of coronavirus package is not up to date:
download.file("https://github.com/RamiKrispin/coronavirus/raw/master/data/coronavirus.rda", destfile="cv")
load("cv")

coronavirus <- coronavirus %>% 
  ungroup() %>%
  mutate(country = if_else(Country.Region=="United Arab Emirates","UAE",Country.Region)) %>%
  mutate(country = if_else(country=="Mainland China", "China", country)) %>%
  mutate(country = if_else(country=="North Macedonia", "N.Macedonia", country)) %>%
  mutate(country = if_else(country=="Iran (Islamic Republic of)", "Iran", country)) %>%
  mutate(country = if_else(country=="Republic of Korea", "South Korea", country)) %>%
  mutate(country = if_else(country=="Russian Federation", "Russia", country)) %>%
  mutate(country = if_else(country=="a", "b", country)) %>%
  mutate(country = trimws(country)) %>%
  mutate(country = factor(country))



#Pivot by Country (Rami Krispin)
df <- coronavirus %>% 
  group_by(Country.Region, country, type) %>%
  summarise(total = sum(cases)) %>%
  pivot_wider(names_from =  type, values_from = total, values_fill = list(total=0))  %>%
  mutate(active = confirmed - recovered - death) %>%
  mutate(recover_rate = recovered / confirmed, death_rate = death / confirmed, active_rate = active / confirmed) %>% 
  arrange(-confirmed) %>%
  ungroup()
  
  
  

#Pivot by Country & Date
df1 <- coronavirus %>% 
  group_by(Country.Region, Lat , Long , country, Province.State, date, type) %>%
  summarise(total = sum(cases)) %>%
  pivot_wider(names_from= type, values_from = total, values_fill = list(total=0)) %>%
  mutate(active = confirmed - recovered - death)



df_iran <- df[df$country=='Iran',]



#Trend (Rami Krispin)
df_daily <- coronavirus %>% 
  group_by(date, type) %>%
  summarise(total = sum(cases, na.rm = TRUE)) %>%
  pivot_wider(names_from = type, values_from = total, values_fill = list(total=0)) %>%
  arrange(date) %>%
  ungroup() %>%
  mutate(active =  confirmed - recovered - death) %>%
  mutate(confirmed_cum = cumsum(confirmed),
         death_cum = cumsum(death),
         recovered_cum = cumsum(recovered),
         active_cum = cumsum(active))


  

trend_iran <- coronavirus %>% 
  filter(Country.Region == 'Iran (Islamic Republic of)') %>%
  group_by(date, type) %>%
  summarise(total = sum(cases, na.rm = TRUE)) %>%
  pivot_wider(names_from = type, values_from = total, values_fill = list(total=0)) %>%
  arrange(date) %>%
  ungroup() %>%
  mutate(active = confirmed - recovered - death) %>%
  mutate(confirmed_cum = cumsum(confirmed),
         death_cum = cumsum(death),
         recovered_cum = cumsum(recovered),
         active_cum = cumsum(active))




max_date <- coronavirus %>% 
  filter(date == max(date)) %>%
  select(Country.Region,country, type, cases) %>%
  group_by(country, type) %>%
  summarise(total = sum(cases)) %>%
  pivot_wider(names_from = type, values_from = total, values_fill = list(total=0)) %>%
  arrange(-confirmed)



min_date <- coronavirus %>%
  ungroup() %>%
  filter(type=='confirmed', cases>0) %>%
  group_by(country) %>%
  summarise(min_date = min(date)) %>%
  arrange(min_date)



cal = seq(from = min(coronavirus$date),
          by = "day",
          length.out = as.numeric(max(coronavirus$date) -min(coronavirus$date))+1)
cal = data.frame(date=cal)

```

WORLD {color=red}
=======================================================================

Row
-----------------------------------------------------------------------
  
### confirmed {.value-box}
  
```{r}

valueBox(value = paste(format(sum(df$confirmed), big.mark = ","), "", sep = " "), 
         caption = "Total Confirmed Cases", 
         icon = "fas fa-user-md", 
         color = confirmed_color)
```


### active {.value-box}

```{r}
valueBox(value = paste(format(sum(df$active), big.mark = ",")
                       ," ("
                       ,round(100 * sum(df$active) / sum(df$confirmed), 1)
                       ,"%)"
                       ,sep = ""), 
         caption = "Active Cases", icon = "fas fa-ambulance", 
         color = active_color)
```

### recovered {.value-box}

```{r}
valueBox(value = paste(format(sum(df$recovered), big.mark = ",")
                       ," ("
                       ,round(100 * sum(df$recovered) / sum(df$confirmed), 1) 
                       ,"%)"
                       ,sep = ""), 
         caption = "Recovered Cases", icon = "fas fa-heartbeat", 
         color = recovered_color)
```

### death {.value-box}

```{r}

valueBox(value = paste(format(sum(df$death), big.mark = ",")
                       ," ("
                       ,round(100 * sum(df$death) / sum(df$confirmed), 1)
                       ,"%)"
                       ,sep = ""),
         caption = "Death Cases", 
         icon = "fas fa-heart-broken", 
         color = death_color)
```




Row
-----------------------------------------------------------------------
  
### Cases Distribution by Type (Top 30 Countries)
  
```{r daily_summary}


plot_ly(data = df[1:30,], 
        x = ~ country, 
        y = ~ active, 
        # text =  ~ confirmed, 
        # textposition = 'auto',
        type = "bar", 
        name = "Active",
        marker = list(color = active_color)) %>%
add_trace(y = ~ recovered, 
          # text =  ~ recovered, 
          # textposition = 'auto',
          name = "Recovered",
          marker = list(color = recovered_color)) %>%
add_trace(y = ~ death, 
          # text =  ~ death, 
          # textposition = 'auto',
          name = "Death",
          marker = list(color = death_color)) %>%
layout(barmode = 'stack',
       yaxis = list(title = "", type = "log"),
       xaxis = list(title = "",
                    categoryorder = "array", categoryarray = ~active+recovered+death),
       hovermode = "compare",
       margin =  list(
                   # l = 60,
                   # r = 40,
                   b = 10,
                   t = 10,
                   pad = 2))





```


Row {data-width=350}
-----------------------------------------------------------------------

### Share of Confirmed Cases till `r  max(coronavirus$date)` {data-width=1}

```{r}
df %>%
  select(country, confirmed) %>%
  plot_ly(labels = ~country, 
        values = ~confirmed,
        type = "pie",
        textposition = 'inside',
        textinfo = 'label+percent',
        #hoverinfo = 'text',
        insidetextfont = list(color = '#FFFFFF'),
        showlegend = FALSE)  %>%
  layout(xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
  


```


#Recovery and Death Rates by Country {data-width=3}
#df_summary <-coronavirus %>% 
#  # dplyr::filter(Country.Region != "Others") %>%
#  dplyr::group_by(Country.Region, type) %>%
#  dplyr::summarise(total_cases = sum(cases)) %>%
#  tidyr::pivot_wider(names_from = type, values_from = total_cases) %>%
#  dplyr::arrange(- confirmed) %>%
#  dplyr::filter(confirmed >= 25) %>%
#  dplyr::select(country = Country.Region, confirmed, recovered, death) %>%
#  dplyr::mutate(recover_rate = recovered / confirmed,
#                death_rate = death / confirmed)  
#df_summary %>%
#  DT::datatable(rownames = FALSE,
#                colnames = c("Country", "Confirmed", "Recovered", "Death", "Recovery #Rate", "Death Rate"),
#                options = list(pageLength = nrow(df_summary), dom = 'tip')) %>%
#  DT::formatPercentage("recover_rate", 2) %>%
#  DT::formatPercentage("death_rate", 2)




### Recovery and Death Rates for Countries with at Least 25 Cases {data-width=3}
  
```{r}
  
df %>%
  filter(confirmed >= 25) %>%
  
  plot_ly(y = ~ round(100 * recover_rate, 1),
          x = ~ round(100 * death_rate, 1),
          size = ~ log(confirmed),
          sizes = c(5, 70),
          type = 'scatter', mode = 'markers',
          color = ~ country,
          marker = list(sizemode = 'diameter' , opacity = 0.5),
          hoverinfo = 'text',
          text = ~paste("", country, 
                        " Confirmed Cases: ", confirmed,
                        " Recovery Rate: ", paste(round(100 * recover_rate, 1), "%", sep = ""),
                        " Death Rate: ",  paste(round(100 * death_rate, 1), "%", sep = ""))) %>%
  layout(yaxis = list(title = "Recovery Rate", ticksuffix = "%"),
         xaxis = list(title = "Death Rate", ticksuffix = "%", 
                      dtick = 1, 
                      tick0 = 0),
         hovermode = "compare")

```   






### Share of Death Cases till `r  max(coronavirus$date)` {data-width=1}

```{r}
df %>%
  select(country, death) %>%
  plot_ly(labels = ~country, 
        values = ~death,
        type = "pie",
        textposition = 'inside',
        textinfo = 'label+percent',
        #hoverinfo = 'text',
        insidetextfont = list(color = '#FFFFFF'),
        showlegend = FALSE)  %>%
  layout(xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
         yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE))
  


```



Trend
=======================================================================

 Row
-----------------------------------------------------------------------


### Daily Cumulative Cases
  
```{r}


plot_ly(data = df_daily) %>%
    add_trace(x = ~ date,
            y = ~ confirmed_cum,
            type = "scatter",
            mode = 'lines+markers',
            name = "Confirmed",
            line = list(color = confirmed_color),
            marker = list(color = confirmed_color)) %>%
  add_trace(x = ~ date,
            y = ~ active_cum,
            type = "scatter",
            mode = "lines+markers",
            name = "Active",
            line = list(color = active_color),
            marker = list(color = active_color)) %>%
  add_trace(x = ~ date,
            y = ~ recovered_cum,
            type = "scatter",
            mode = "lines+markers",
            name = "Recovered",
            line = list(color = recovered_color),
            marker = list(color = recovered_color)) %>%
  add_trace(x = ~ date,
            y = ~ death_cum,
            type = "scatter",
            mode = 'lines+markers',
            name = "Death",
            line = list(color = death_color),
            marker = list(color = death_color)) %>%
  add_annotations(x = as.Date("2020-03-01"),
                  y = 42716,
                  text = paste("# of recovered cases surpass", 
                               "", 
                               "the # of active cases"),
                  xref = "x",
                  yref = "y",
                  arrowhead = 5,
                  arrowhead = 3,
                  arrowsize = 1,
                  showarrow = TRUE,
                  ax = -10,
                  ay = 90) %>%
  layout(title = "",
         yaxis = list(title = "Cumulative No. of Cases"),
         xaxis = list(title = ""),
         legend = list(x = 0.1, y = 0.9),
         hovermode = "compare")

```





### Daily New Confirmed Cases - China vs. Rest of the World

```{r}
daily_confirmed <- coronavirus %>%
  filter(type == "confirmed") %>%
  mutate(country = dplyr::if_else(Country.Region == "Mainland China", 
                                  "China", 
                                  "Rest of the World")) %>%
  group_by(date, country) %>%
  summarise(total = sum(cases)) %>% 
  ungroup() %>%
  pivot_wider(names_from = country, values_from = total) 

#----------------------------------------
# Plotting the data

daily_confirmed %>%
  plot_ly() %>% 
  add_trace(x = ~ date, 
            y = ~ China, 
            type = "scatter", 
            mode = "lines+markers",
            name = "China") %>% 
  add_trace(x = ~ date, 
            y = ~ `Rest of the World`, 
            type = "scatter", 
            mode = "lines+markers",
            name = "Rest of the World") %>% 
  add_annotations(x = as.Date("2020-02-13"),
                  y = 15133,
                  text = paste("China modified the diagnostic criteria"),
                  xref = "x",
                  yref = "y",
                  arrowhead = 5,
                  arrowhead = 3,
                  arrowsize = 1,
                  showarrow = TRUE,
                  ax = 50,
                  ay = -40) %>%
  layout(title = "",
         legend = list(x = 0.1, y = 0.9),
         yaxis = list(title = "Number of New Cases"),
         xaxis = list(title = ""),
         # paper_bgcolor = "black",
         # plot_bgcolor = "black",
         # font = list(color = 'white'),
         hovermode = "compare",
         margin =  list(
                        # l = 60,
                        # r = 40,
                        b = 10,
                        t = 10,
                        pad = 2
                 ))

```





Row
-----------------------------------------------------------------------


### How many countries have encountered coronavirus?
  
```{r}


a=cal%>%
  mutate(No.Countries=rep(NA,length(cal)))


for (val in cal$date ) {
  a[a$date==val,]$No.Countries = sum(min_date$min_date<=val)
  }


a %>%
  plot_ly(x = ~ date, 
          y = ~ No.Countries, 
          type = "scatter", 
          mode = "lines+markers",
          name = "No.Countries",
          line = list(color = confirmed_color),
          marker = list(color = confirmed_color)) %>% 
  layout(xaxis = list(title = ''),
         yaxis = list(title = 'Number of Countires'),
         hovermode = "compare")





``` 




### How many countries have at least one active case at the time?

```{r}

b = cal%>%
  mutate(No.Countries=rep(NA,length(cal)))  
 
df1 %>%
  ungroup() %>%
  select(date, country, active) %>%
  arrange(country, date) %>%
  group_by(country, date) %>%
  summarise(active=sum(active)) %>%
  mutate(activ_cum=ave(active, country, FUN=cumsum)) %>%
  filter(activ_cum>0) %>%
  select(date, country) %>%
  group_by(date) %>%
  summarise(No.Countries =  n()) %>%
  arrange(date) %>%


plot_ly(x = ~ date, 
        y = ~ No.Countries, 
        type = "scatter", 
        mode = "lines+markers",
        name = "No.Countries",
        line = list(color = active_color),
        marker = list(color = active_color)) %>% 
layout(xaxis = list(title = ''),
       yaxis = list(title = 'Number of Countires'),
       hovermode = "compare")


  
  
``` 



Today
=======================================================================


Row
-----------------------------------------------------------------------

### Cases Status Update for `r  max(coronavirus$date)`
  
```{r}



  max_date %>%  
  DT::datatable(rownames = FALSE,
                colnames = c("Country", "Confirmed", "Recovered", "Death"),
                options = list(pageLength = 10, dom = 'tip', searchHighlight = TRUE),
                filter = 'top')
  

```



### New Confirmed Cases on `r  max(coronavirus$date)` - Top 15 Countries
```{r}

max_date %>%
  ungroup() %>%
  arrange(-confirmed) %>%
  filter(confirmed > 0) %>%
  top_n(n = 15, wt = confirmed) %>%
  
  plot_ly(x = ~ country,
          y = ~ confirmed,
          text = ~ confirmed,
          textposition = 'auto',
          type = "bar",
          marker = list(color = confirmed_color)) %>%
  layout(yaxis = list(title = ""), #paste("Confirmed Cases on ", max(coronavirus$date))),
         xaxis = list(title = "",
                      categoryorder = "array", categoryarray = ~confirmed),
         margin =  list(
         l = 10,
         r = 10,
         b = 10,
         t = 10,
         pad = 2
         ))

  
```



Row
-----------------------------------------------------------------------

### New Recovered Cases on `r  max(coronavirus$date)` - Top 15 Countries
```{r}

max_date %>%
  ungroup() %>%
  arrange(-recovered) %>%
  filter(recovered > 0) %>%
  top_n(n = 15, wt = recovered) %>%
  
  plot_ly(x = ~ country,
          y = ~ recovered,
          text = ~ recovered,
          textposition = 'auto',
          type = "bar",
          marker = list(color = recovered_color)) %>%
  layout(yaxis = list(title = ""),
         xaxis = list(title = "",
                      categoryorder = "array", categoryarray = ~recovered),
         margin =  list(
         l = 10,
         r = 10,
         b = 10,
         t = 10,
         pad = 2
         ))


```

### New Death Cases on `r  max(coronavirus$date)` - Top 15 Countries
```{r}

max_date %>%
  ungroup() %>%
  arrange(-death) %>%
  filter(death > 0) %>%
  top_n(n = 15, wt = death) %>%
  
  plot_ly(x = ~ country,
          y = ~ death,
          text = ~ death,
          textposition = 'auto',
          type = "bar",
          marker = list(color = death_color)) %>%
  layout(yaxis = list(title = ""),
         xaxis = list(title = "",
                      categoryorder = "array", categoryarray = ~death),
         margin =  list(
         l = 10,
         r = 10,
         b = 10,
         t = 10,
         pad = 2
         ))


```



Map
=======================================================================

<center>Coronavirus Confirmed Cases Worldwide</center>

```{r}

# light grey boundaries
l <- list(color = toRGB("grey"), width = 0.1)

# specify map projection/options
g <- list(
  showframe = FALSE,
  showcoastlines = FALSE,
  projection = list(type = 'Mercator')
)

df %>%
  plot_geo(z = ~ log(confirmed), 
           color = ~ confirmed, 
           colors = 'Purples',
           text = ~ paste(country, ' >> ', confirmed), 
           hoverinfo = 'text',
           locations = ~ country , 
           locationmode = 'country names',
           marker = list(line = l)) %>%

  #colorbar(title = 'Confirmed Cases', tickprefix = '') %>%
  hide_colorbar() %>% 
  layout(geo = g)
         #title = '2014 Global GDP<br>Source:<a href="https://www.cia.gov/library/publications/the-world-factbook/fields/2195.html">CIA World Factbook</a>'




```


IRAN
=======================================================================



Row
-----------------------------------------------------------------------

### confirmed {.value-box}
  
```{r}

valueBox(value = paste(format(sum(df_iran$confirmed), big.mark = ","), "", sep = " "), 
         caption = 'Mobtala shodegan',
         icon = "fas fa-user-md", 
         color = confirmed_color)
```


### active {.value-box}

```{r}
valueBox(value = paste(format(sum(df_iran$active), big.mark = ",")
                       ," ("
                       ,round(100 * sum(df_iran$active) / sum(df_iran$confirmed), 1)
                       ,"%)"
                       ,sep = ""), 
         caption = 'Mobtalayan tayin taklif nashode',
         icon = "fas fa-ambulance", 
         color = active_color)
```

### recovered {.value-box}

```{r}
valueBox(value = paste(format(sum(df_iran$recovered), big.mark = ",")
                       ," ("
                       ,round(100 * sum(df_iran$recovered) / sum(df_iran$confirmed), 1) 
                       ,"%)"
                       ,sep = ""), 
         caption = "Behbud yaftegan", icon = "fas fa-heartbeat", 
         color = recovered_color)
```

### death {.value-box}

```{r}

valueBox(value = paste(format(sum(df_iran$death), big.mark = ",")
                       ," ("
                       ,round(100 * sum(df_iran$death) / sum(df_iran$confirmed), 1)
                       ,"%)"
                       ,sep = ""),
         caption = "Fot shodegan", 
         icon = "fas fa-heart-broken", 
         color = death_color)
```



 Row
-----------------------------------------------------------------------


### Daily Cumulative Cases in Iran {data-width=4}
  
```{r}

df1 %>%
  ungroup() %>%
  filter(country=='Iran') %>%
  select(date, recovered, death, active) %>%
  mutate(recovered_cum=cumsum(recovered),
         death_cum=cumsum(death),
         active_cum=cumsum(active)) %>%

  plot_ly(x = ~ date,
          y = ~ active_cum,
          type = "scatter",
          mode = "lines+markers",
          name = "Active",
          line = list(color = active_color),
          marker = list(color = active_color)) %>%
  add_trace(x = ~ date,
            y = ~ recovered_cum,
            type = "scatter",
            mode = "lines+markers",
            name = "Recovered",
            line = list(color = recovered_color),
            marker = list(color = recovered_color)) %>%
  add_trace(x = ~ date,
            y = ~ death_cum,
            type = "scatter",
            mode = 'lines+markers',
            name = "Death",
            line = list(color = death_color),
            marker = list(color = death_color)) %>%
  layout(title = "",
         yaxis = list(title = "Cumulative No. of Cases"),
         xaxis = list(title = ""),
         legend = list(x = 0.1, y = 0.9),
         hovermode = "compare")

```




### Population (www.worldometers.info) {data-width=2}
```{r}

as.data.frame(cbind(c('China','Iran','Italy','South Korea'),
                    c('1439','84','60','51'))) %>%
  DT::datatable(class='compact',
            colnames = c('Country', 'Population in Millions'),
            options = list(sDom = '<"top"><"bottom">'))



```



### Cumulative Confirmed Cases - Top 3 Countries Excluding China {data-width=4}
```{r}

#top <- df %>%
#  filter(country!='China') %>%
#  arrange(-confirmed) %>%
#  top_n(3, wt=confirmed) %>%
#  select(country)

df1 %>%
  ungroup() %>%
  #filter(country %in% unlist(top)) %>%
  filter(country %in% c('Iran', 'Italy', 'South Korea')) %>%
  select(country, date, confirmed) %>%
  arrange(country, date) %>%
  mutate(confirmed_cum = ave(confirmed, country, FUN=cumsum)) %>%
  select(country, date, confirmed_cum) %>%
  pivot_wider(names_from = country,
              values_from = confirmed_cum,
              values_fill=list(confirmed_cum=0)) %>%
  arrange(date) %>%


  plot_ly(x = ~ date,
          y = ~ Iran,
          type = "scatter",
          mode = "lines+markers",
          name = "Iran",
          line = list(color = 'green'),
          marker = list(color = 'green')) %>%
  
  add_trace(x = ~ date, 
            y = ~ Italy, 
            type = "scatter", 
            mode = "lines+markers",
            name = "Italy",
            line = list(color = 'blue'),
            marker = list(color = 'blue')) %>% 
  
  add_trace(x = ~ date, 
            y = ~ `South Korea`, 
            type = "scatter", 
            mode = "lines+markers",
            name = "South Korea",
            line = list(color = 'red'),
            marker = list(color = 'red')) %>% 

  layout(title = "",
         yaxis = list(title = "Cumulative Confirmed Cases"),
         xaxis = list(title = ""),
         legend = list(x = 0.1, y = 0.9),
         hovermode = "compare")




```




 Row
-----------------------------------------------------------------------

### Age and Gender Distribution - Confirmed Cases


As soon as I access respective data!



### Gender - Confirmed Cases

As soon as I access respective data!


Data
=======================================================================

```{r}
df1 %>% 
  ungroup() %>%
  select(date, country, Province.State, confirmed, recovered, death) %>%
  DT::datatable(rownames = FALSE,
                options = list(searchHighlight = TRUE, pageLength = 20), 
                filter = 'top')
```



About
=======================================================================
  
**The Coronavirus Dashboard**

  This analysis dashboard provides some visualizations on coronavirus pandemic disease (COVID-19). It's developed via R with the help of Rmarkdown framework.

  
  
**Data**
  
  The input data for this dashboard is the [coronavirus](https://github.com/RamiKrispin/coronavirus) R package (dev version). The data and dashboard is refreshed on a daily bases. The raw data pulled from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus [repository](https://github.com/RamiKrispin/coronavirus-csv)



**Deployment and Reproducibly**
  
  The dashboard was deployed to Github docs. If you wish to deploy and/or modify the dashboard on your Github account, you can apply the following steps:
  
* Fork the dashboard [repository](https://github.com/RamiKrispin/coronavirus_dashboard), or
* Clone it and push it to your Github package
* Here some general guidance about deployment of flexdashboard on Github page - [link](https://github.com/pbatey/flexdashboard-example)



**About Me**

  My name is Hadi Jafari. I've always been passionate about analyzing data. Having this in mind, these days most of the countries in the world are fighting with coronavirus. This drew my attention and raised some questions regarding the fact and figures. I happened to see some great visualizations developed by dear [Rami Krispin](https://ramikrispin.github.io/). I still had other questions on my mind to be answered. So I decided to expand Rami Krispin's work.
  Check this dashboard and let me know if you've got any question or feedback. You can contact me on [Linkedin](https://www.linkedin.com/in/hadi-jafari/).
  I do hope conditions improve worldwide ASAP.
